Hypertension and microbiome

### 2019-06-12 articletwo.Rmd
Round 3

```{r salt characteristics}
pseq.genus.salt %>%
    meta %>%
    gather(key,value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       sd = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    mutate_if(is.numeric, round, 2) %>%
    kable()
```

>>>>

```{r salt characteristics}
pseq.genus.salt %>%
    meta %>%
    gather(key,value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       sd = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    mutate_if(is.numeric, round, 3) %>%
    kable()
```
